

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Professional Skills}

\cvskill{C++}{5}
\cvskill{Python}{4}
\cvskill{HLS}{4}
\cvskill{Arduino}{3}
\cvskill{Pandas}{3}
\cvskill{CERN ROOT}{3}
\cvskill{Bash}{3}
\cvskill{CUDA}{2}~\\
% \cvskill{Javascript}{2}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Strengths %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Strengths}

\begin{itemize}
\item \textcolor{emphasis}{Development tools} 
\end{itemize}
\cvtag{Vivado HLS}\cvtag{GDB \& PDB debugger}\cvtag{Visual Studio Code}\cvtag{Git}\cvtag{Continuous integration}\cvtag{SSH}\cvtag{Vim}
\divider

\begin{itemize}
\item \textcolor{emphasis}{Platforms}
\end{itemize}
\cvtag{Linux}\cvtag{Xilinx FPGA}
% \divider

% \begin{itemize}
% \item \textcolor{emphasis}{Development Tools -- IDE}
% \end{itemize}
% \cvtag{Visual Studio}\cvtag{VS Code}\cvtag{IntelliJ}\cvtag{XCode}
% \divider\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Softskills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Soft skills}

% \cvtag{Problem solving}
% \cvtag{Problem modelling}
\cvtag{Debugging}
\cvtag{Team Work}
\cvtag{Flexibility}
\cvtag{Creativity}
\cvtag{Work Under Pressure}
\cvtag{Organization}
\cvtag{Responsibility}
% \cvtag{Professionalism}
% \cvtag{MultiTasking}
% \cvtag{Agile}
% \cvtag{Scrum}

\cvsection{Publications \& talks}

\begin{enumerate}
  \item \small{FCC collaboration, Future Circular Collider Study. Volume 3: The Hadron Collider (FCC-hh) Conceptual Design Report, CERN-ACC-2018-0058, Geneva, December 2018. Published in Eur. Phys. J. ST., p. 973-975}
  \item \small{S. Bologna et al. “Trigger \& Data Acquisition at FCC-hh”. Talk at the FCC Week 2017, Berlin. 29th May - 2nd June 2017. 
URL: \url{https://indico.cern.ch/event/556692/contributions/2465162/}}
  \item \small{S. Bologna et al. “Trigger \& Data Acquisition at FCC-hh”. Talk at the FCC Week 2018, Amsterdam. 12th April 2018. 
URL: \url{https://indico.cern.ch/event/656491/contributions/2923411/}}
\item \small{CMS Collaboration, The Phase-2 Upgrade of the CMS Level-1 Trigger, Tech. Rep. 1274, CERN-LHCC-2020-004. CMS-TDR-021, CERN, Geneva, Apr 2020.}
\end{enumerate}

\cvsection{Languages}
\cvskill{English}{5}
\cvskill{Italian}{5}
\cvskill{French}{2}